---
title: "Final Project - Greenspace and Wellbeing"
author: "Wylie Hampson"
date: "11/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

### Import the data

```{r}
data <- read_csv(here("data", "greenspace_data.csv")) %>% 
  clean_names()
```

### I am interested in particular how having windows in their bedrooms affects college and graduate students. So from this data set I will filter out only the people who are 35 and younger, since that will more similarly represent students.

```{r}
under35 <- data %>% 
  filter(age <= 35)
```

### Next, I'll make a well-being column that adds up the values for life satisfaction, self-esteem, and subjective happiness. Then, subtracts values from the depression and anxiety column, and the lonliness column. This will give one value for a persons overall well being.

```{r}
under35 <- under35 %>% 
  mutate(well_being = (life_satisfaction + self_esteem + subjective_happiness) - (depression_and_anxiety + loneliness))
```

### Plot a histogram of the well-being values.

```{r}
ggplot(data = under35, aes(x = well_being)) +
  geom_histogram()
```

### Make a scatter plot of well-being versus whether or not a person has a window in their room.

```{r}
under35 <- under35 %>% 
  mutate(nature_view = as.logical(nature_view))

ggplot(data = under35, aes(x = nature_view, y = well_being)) +
  geom_boxplot(aes(color = nature_view))
```

```{r}
mu_window <- under35 %>% 
  filter(nature_view == TRUE) %>% 
  summarize(mean(well_being))

mu_no_window <- under35 %>% 
  filter(nature_view == FALSE) %>% 
  summarize(mean(well_being))

point_est <- as.numeric(mu_window - mu_no_window)
```


```{r}
n_window = under35 %>% filter(nature_view == TRUE) %>% count()
n_no_window = under35 %>% filter(nature_view == FALSE) %>% count()
sd_window = under35 %>% filter(nature_view == TRUE) %>% summarize(sd(well_being, na.rm = TRUE))
sd_no_window = under35 %>% filter(nature_view == FALSE) %>% summarize(sd(well_being, na.rm = TRUE))
SE = as.numeric(sqrt(sd_window ^ 2 / n_window + sd_no_window ^ 2 / n_no_window))
print(SE)

```

```{r}
zscore <- point_est / SE

p_val <- 2 * pnorm(point_est, mean = 0, sd = SE, lower.tail = FALSE)
p_val
```

```{r}
t.test(well_being ~ nature_view, data = under35)
```

### Now let's see if going outside interacts as well.

```{r}
ggplot(data = under35, aes(x = greenspace_use_frequency, y = well_being)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE)

summary(lm(data = under35, well_being ~ greenspace_use_frequency))
```
```{r eval = FALSE}
mod <- lm(well_being ~ greenspace_use_frequency + nature_view, data = under35)
```

```{r}
ggplot(data = under35, aes(x = greenspace_use_frequency, y = well_being, color = nature_view)) +
  geom_point() +
  geom_line(data = augment(mod), aes(y = .fitted, color = nature_view))

summary(mod)
```





