---
title: "Final Project - Greenspace and Wellbeing"
author: "Wylie Hampson"
date: "11/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

### Import the data

```{r}
data <- read_csv(here("data", "greenspace_data.csv")) %>% 
  clean_names()
```

### I am interested in particular how having windows in their bedrooms affects college and graduate students. So from this data set I will filter out only the people who are 35 and younger, since that will more similarly represent students.

```{r}
under35 <- data %>% 
  filter(age <= 35)
```

### Next, I'll make a well-being column that adds up the values for life satisfaction, self-esteem, and subjective happiness. Then, subtracts values from the depression and anxiety column, and the lonliness column. This will give one value for a persons overall well being.

```{r}
under35 <- under35 %>% 
  mutate(well_being = (life_satisfaction + self_esteem + subjective_happiness) - (depression_and_anxiety + loneliness))
```

### Plot a histogram of the well-being values.

```{r}
ggplot(data = under35, aes(x = well_being)) +
  geom_histogram()
```

### Make a scatter plot of well-being versus whether or not a person has a window in their room.

```{r}
under35 <- under35 %>% 
  mutate(nature_view = as.logical(nature_view))

ggplot(data = under35, aes(x = nature_view, y = well_being)) +
  geom_violin(aes(color = nature_view))
```

